\section{Problem C}
\textit{REDUCING MAXIMUM PATH LOSS. For the same given coverage area, compare the maximum path loss of a single antenna system, $PL_{max^1}$, to the maximum path loss of an M-antenna distributed system, $PL_{max^M}$, and express the reduction in the dynamic range. Define path loss at the cell boundary, $d_c$, of the single-antenna system (as in the boxed expression above). State the implications of the relation.}\\

The maximum pathloss is given by:
\begin{flalign}
&& PL_{max} \equiv & \frac{P_R}{P_{d_c}} = C\left(\frac{A_c}{\pi}\right)^{\sfrac{\gamma}{2}} & \label{eq:MaximumPathLoss}
\end{flalign}  

where $PL_{max}$ is the maximum pathloss, $P_R$ is the reference power which is equivalent to the transmitted power and $P_{d_c}$ is the minimum acceptable downlink power level at the cell boundary which is at the distance $d_c$ from the cell center (Radius of coverage area). $A_c$ is the coverage area of the cell and $\gamma$ is the pathloss exponent. C is a scaling constant. \\

From the hint given in the exercise we can derive the following:
\begin{flalign}
&& \frac{PL_{max}^M}{PL_{max}^1}  =& \frac{P_{R}^M}{P_{R}^1} = \frac{P_{R}^1}{P_{R}^1 \cdot M} = \frac{1}{M} & \label{eq:hintTBS} 
\end{flalign}

Using this relation we can combine it with area relation from \secref{sec:mm3_PbA} and shown in \equref{eq:ExpressionForAcWithM} where the relation between  number of antennas ($M$) and the area ($A_c$) is found. This is shown in the following:
\begin{flalign}
&& PL_{max}^M  =& \frac{C}{\pi} \, \left(A_{C}^M\right)^{\frac{\gamma}{2}} = \frac{C}{\pi} \, \left(A_{C}^1\right)^{\frac{\gamma}{2}} \, \left(M^{-\frac{2}{\gamma}}\right)^{\frac{\gamma}{2}}  = \frac{1}{M}\, PL_{max}^1 & 
\end{flalign}
This shows the relation to \equref{eq:hintTBS} giving that these are equivalent.
